target_offtarget

### 2025-07-08 manuscript_figures.Rmd
Update Figure S15

persite_both |>
  filter(virus == "cardiovirus") |>
  filter(mapper == "bowtie2") |>
  filter(type == "dedup") |>
  filter(Background != "p6") |>
  ggplot(aes(
    x = site,
    y = coverage,
    fill = Background
  )) +
  geom_col() +
  facet_wrap(Viral.load ~ Sample_id, labeller = label_parsed) +
  scale_fill_manual(values = cols2, labels = c("M1", "M2")) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "right",
    panel.grid.major = element_line(linewidth = 0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth = 0.1, color = "lightgray")
  ) +
  ylab("Coverage") +
  xlab("") +
  ggtitle("Cardiovirus") +
  scale_y_log10(labels = scales::trans_format("log10",
                                              scales::label_math()))
```

>>>>

persite_both |>
  filter(virus == "cardiovirus") |>
  filter(mapper == "bowtie2") |>
  filter(type == "dedup") |>
  filter(Background != "p6") |>
  ggplot(aes(
    x = site,
    y = (coverage),
    fill = Background
  )) +
  geom_col() +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "right",
    panel.grid.major = element_line(linewidth = 0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth = 0.1, color = "lightgray")
  ) +   
  facet_wrap(Viral.load ~ Sample_id, labeller = label_parsed) +
  scale_fill_manual(values = cols2, labels = c("M1", "M2")) +
  ylab("Coverage") +
  xlab("") +
  ggtitle("Cardiovirus") +
  scale_y_log10(labels = scales::trans_format("log10",
                                              scales::label_math()))
```
